AGB Stars in the IR: Physical Characteristics, Galactic Spatial Distribution, and Chemical Impact of the Milky Way AGB Population

### 2015-05-05 paper1/paper1_intro.tex
ZI edits

\section{Introduction}
The formation of galaxies like the \mw\, was long thought to be a steady process that created a smooth distribution of stars. This standard view was exemplified by the \cite{1980ApJS...44...73B} and \cite{1989ARA&A..27..555G} models, described in detail by, e.g., \cite{1993ARA&A..31..575M}. It was further motivated by observations of other galaxies, as well as what little information was available from \emph{High Precision Parallax Collecting Satellite} \citep[\emph{HIPPARCOS}, ][]{1984SSRv...39....1K} and smaller pencil-beam surveys. In these, the \mw\, is modeled by three discrete components described by simple analytic expressions: the thin disk, thick disk, and halo.

>>>>

\section{Introduction}

- brief intro to Gal structure

- SDSS and other recent results do not go into the plane

- mention a few studies that do (GLIMPSE etc) and ongoing data taking with DECam

- AGB stars: luminous in IR, relatively easy to find; mention MACHO and OGLE studies, 
   refer to Jackson et al. IRAS-based study, lead to WISE

- brief description of WISE

- paper outline

The formation of galaxies like the \mw\, was long thought to be a steady process that created a smooth distribution of stars. This standard view was exemplified by the \cite{1980ApJS...44...73B} and \cite{1989ARA&A..27..555G} models, described in detail by, e.g., \cite{1993ARA&A..31..575M}. It was further motivated by observations of other galaxies, as well as what little information was available from \emph{High Precision Parallax Collecting Satellite} \citep[\emph{HIPPARCOS}, ][]{1984SSRv...39....1K} and smaller pencil-beam surveys. In these, the \mw\, is modeled by three discrete components described by simple analytic expressions: the thin disk, thick disk, and halo.

Review is \citet{IBJ2012} \citep{IBJ2012}
